Impact of IPTp Regimen on Pregnancy Outcomes in a Malaria-Endemic Setting

### 2025-04-28 code/analysis-code/Statistical_Analysis.qmd
P3

# Machine learning & modeling
library(tidymodels)         # Modeling framework (recipes, parsnip, workflows, tune, yardstick, rsample)
library(themis)             # Class-imbalance sampling (e.g., SMOTE)
library(dials)              # Parameter tuning grids
library(ranger)             # Random forest engine
library(xgboost)            # Gradient boosting engine
library(generalhoslem)
library(ResourceSelection)
library(rms)
library(car)

@@

@@

```{r}
# Load necessary libraries
library(dplyr)
library(gtsummary)
library(here)

# Read in the cleaned data (if not already read)
promo_data_clean <- read.csv(here("data", "clean", "PROMO_Data_clean.csv"))

>>>>

# Machine learning & modeling
library(tidymodels)         # Modeling framework (recipes, parsnip, workflows, tune, yardstick, rsample)
library(themis)             # Class-imbalance sampling (e.g., SMOTE)
library(dials)              # Parameter tuning grids
library(ranger)             # Random forest engine
library(xgboost)            # Gradient boosting engine
library(generalhoslem)
library(ResourceSelection)
library(rms)
library(car)
```

@@

```{r}
# Load the cleaned data
promo_data_clean <- read.csv(here("data", "clean", "PROMO_Data_clean.csv"))

# 1. Check the class of the variable
class(promo_data_clean$preterm_births_count)

# 2. View its internal structure
str(promo_data_clean$preterm_births_count)

# 3. Get basic summary statistics
summary(promo_data_clean$preterm_births_count)

# 4. Tabulate all observed values (including NAs)
table(promo_data_clean$preterm_births_count, useNA = "always")

# 5. Quick glimpse using dplyr (avoids calling select on a vector)
glimpse(promo_data_clean %>% select(preterm_births_count))
```

@@

```{r}
# Read in the cleaned data (if not already read)
promo_data_clean <- read.csv(here("data", "clean", "PROMO_Data_clean.csv"))
